Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-06-02 paper/AlignedIsotropicGW.tex
Close #47, three, not two, years to 10 detections.

Estimates of the rate of \ac{BBH} coalescences give a reasonable
chance of 10 additional \ac{BBH} detections in the next two
years\cite{O1-BBH,2016ApJ...833L...1A,2016ApJS..227...14A}.  Assuming
10 additional detections drawn from each of our six zero-parameter
models for the spin distribution in addition to the three existing
detections from O1, with observational uncertainties drawn randomly
from the three Gaussian widths used to approximate the $\chieff$
posteriors in Figure \ref{fig:O1-posteriors}\footnote{The measurement
  uncertainty in $\chieff$ depends on the other parameters of the
  merging \ac{BBH} system, particularly on the mass ratio.  Our
  assumption about future observational uncertainties is appropriate
  if the parameters of the three detected events are representative of
  the parameters of future detections. See Methods Section
  \ref{sec:chi-eff-precision} for further discussion.}, we find the
odds ratios shown in Figure \ref{fig:O2-predictions}.  We find that
most scenarios with an additional 10 detections allow the simulated
angular distribution to be inferred with greater than $5\sigma$
($2.9 \times 10^{-7}$ odds) credibility; and in the most pessimistic
case the distinction is typically $\OTwoSigmaIsoAlignedMin\sigma$
($\OTwoOddsIsoAlignedMin$ odds ratio).  While such future detections
should permit a confident distinction between \emph{angular}
distributions, we would remain much less certain about the
\emph{magnitude} distribution among the three options considered here
until we have a larger number of
observations\cite{2017arXiv170306869F,2017arXiv170306223G}.  In Figure
\ref{fig:O2-predictions}, the odds ratio between different magnitude
distributions with the same angular distribution is much closer to
unity than the odds ratio between angular distributions.

>>>>

Estimates of the rate of \ac{BBH} coalescences give a reasonable
chance of 10 additional \ac{BBH} detections in the next three
years\cite{O1-BBH,2016ApJ...833L...1A,2016ApJS..227...14A}.  Assuming
10 additional detections drawn from each of our six zero-parameter
models for the spin distribution in addition to the three existing
detections from O1, with observational uncertainties drawn randomly
from the three Gaussian widths used to approximate the $\chieff$
posteriors in Figure \ref{fig:O1-posteriors}\footnote{The measurement
  uncertainty in $\chieff$ depends on the other parameters of the
  merging \ac{BBH} system, particularly on the mass ratio.  Our
  assumption about future observational uncertainties is appropriate
  if the parameters of the three detected events are representative of
  the parameters of future detections. See Methods Section
  \ref{sec:chi-eff-precision} for further discussion.}, we find the
odds ratios shown in Figure \ref{fig:O2-predictions}.  We find that
most scenarios with an additional 10 detections allow the simulated
angular distribution to be inferred with greater than $5\sigma$
($2.9 \times 10^{-7}$ odds) credibility; and in the most pessimistic
case the distinction is typically $\OTwoSigmaIsoAlignedMin\sigma$
($\OTwoOddsIsoAlignedMin$ odds ratio).  While such future detections
should permit a confident distinction between \emph{angular}
distributions, we would remain much less certain about the
\emph{magnitude} distribution among the three options considered here
until we have a larger number of
observations\cite{2017arXiv170306869F,2017arXiv170306223G}.  In Figure
\ref{fig:O2-predictions}, the odds ratio between different magnitude
distributions with the same angular distribution is much closer to
unity than the odds ratio between angular distributions.
